IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-05 ms_infocus.tex
Minor edits to Acknowledgements.
Added comment package.
Minor edits headings and address.
Advancing the Intro.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 8165 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\noindent \textbf{Keywords:} Lorem ipsum, dolor sit amet, consectetuer, adipiscing,
suspendisse

@@

%---------------------------------------------------------------------------------
 "There is a Madagascar Orchis--the Angræcum sesquipedale--with an immensely long and deep nectary. How did such an extraordinary organ come to be developed? Mr. Darwin's [[p. 475]] explanation is this. The pollen of this flower can only be removed by the proboscis of some very large moths trying to get at the nectar at the bottom of the vessel. The moths with the longest proboscis would do this most effectually; they would be rewarded for their long noses by getting the most nectar; whilst on the other hand, the flowers with the deepest nectaries would be the best fertilized by the largest moths preferring them. Consequently, the deepest nectaried Orchids and the longest nosed moths would each confer on the other a great advantage in the 'battle of life.' This would tend to their respective perpetuation and to the constant lengthening of nectar and noses."

@@

My work was funded by a Severo-Ochoa Excellence Grant (SEV2012-0262) from the Spanish Ministerio de Econom\'ia y Competitividad (MINECO), and RNM-5731 from the Junta de Andaluc\'ia.

@@

\bibitem{Borrell:2005}
Borrell, B. (2005) Long tongues and loose niches: Evolution of euglossine bees and their nectar flowers. Biotropica, 37, 664–669.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%---------------------------------------------------------------------------------

\begin{flushright}
  \noindent 
  		\textbf{Pedro Jordano }\\
		\textit{Integrative Ecology Group, Estaci\'on Biol\'ogica de Do\~nana, \\ Consejo Superior de Investigaciones Cient\'ificas (EBD-CSIC), \\ Avenida Americo Vespucio s\slash n, \\ E--41092 Sevilla, Spain}
\end{flushright}
\newpage

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms, a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: Andrea Cocucci. An sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=14cm]{Fig1}
  \end{center}
\end{figure}
%---------------------------------------------------------------------------------

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 8165 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\noindent \textbf{Keywords:} complex networks, forbidden links, long-tubed flowers, mutualism, pollination, Sphingidae

@@

%---------------------------------------------------------------------------------
Size-limited foragers show clear restrictions on the size of prey items they can efficiently handle. In the case of plant-pollinator interactions, size uncoupling between pollinator bodies and flower sizes or structure are specially relevant in filtering out a range of potential partners \citep{Cocucci:2009}. The idea, when applied to the bizarre flowers of some plants pollinated by sphingid moths (Lepidoptera: Sphingidae), was seminal in Darwinian evolutionary theory to support the potential of natural selection in shaping adaptations. Wallace \citep{Wallace:1867} in his book, \textit{Creation by law}, vividly uses the famous example of the Malagasy orchid and its sphingid pollinator to refute the arguments of the Duke of Argyll against natural selection and Darwinism:

\begin{spacing}{1.0}
	\begin{quotation}
	 "There is a Madagascar Orchis--the \textit{Angræcum sesquipedale}--with an immensely long and deep nectary. How did such an extraordinary organ come to be developed? Mr. Darwin's [[p. 475]] explanation is this. The pollen of this flower can only be removed by the proboscis of some very large moths trying to get at the nectar at the bottom of the vessel. The moths with the longest proboscis would do this most effectually; they would be rewarded for their long noses by getting the most nectar; whilst on the other hand, the flowers with the deepest nectaries would be the best fertilized by the largest moths preferring them. Consequently, the deepest nectaried Orchids and the longest nosed moths would each confer on the other a great advantage in the 'battle of life.' This would tend to their respective perpetuation and to the constant lengthening of nectar and noses."
	 \end{quotation}
 \end{spacing}

 Phenotypic fitting of corolla length and shape and pollinators' feeding apparatus and body sizes are important because the better the fit, the better the consequences in terms of fitness outcomes for the interaction partners \citep{Nilsson:1988}. Yet the expectation of perfect trait matching across populations or communities is too simplistic \citep{Anderson:2010}.

@@

My work was funded by a Severo-Ochoa Excellence Grant (SEV2012-0262) from the Spanish Ministerio de Econom\'ia y Competitividad (MINECO), and RNM-5731 from the Junta de Andaluc\'ia. Andrea Cocucci generously provided material for Fig. 1 and insightful discussions on sphingids and long-tubed flowers.

@@

@@

\bibitem{Wallace:1867}
Wallace, A.R. (1867) Creation by law. The Quarterly Journal of Science, 4, 471–488.

\bibitem{Nilsson:1988}
Nilsson, L.A. (1988) The evolution of flowers with deep corolla tubes. Nature, 334, 147–149.

\bibitem{Anderson:2010}
Anderson, B., Terblanche, J.S. \& Ellis, A.G. (2010) Predictable patterns of trait mismatches between interacting plants and insects. BMC Evolutionary Biology, 10, 204.

@@

\begin{flushright}
  \noindent 
  		\textbf{Pedro Jordano }\\
  		\begin{spacing}{1.0}
		\textit{Integrative Ecology Group, Estaci\'on Biol\'ogica de Do\~nana, \\ Consejo Superior de Investigaciones Cient\'ificas (EBD-CSIC), \\ Avenida Americo Vespucio s\slash n, \\ E--41092 Sevilla, Spain}
		\end{spacing}
\end{flushright}
\newpage

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms, a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: Andrea Cocucci. An sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=14cm]{Fig1}
  \end{center}
\end{figure}
%---------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MS NOTES
\begin{comment}
\bibitem{Borrell:2005}
Borrell, B. (2005) Long tongues and loose niches: Evolution of euglossine bees and their nectar flowers. Biotropica, 37, 664–669.

\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
